Data Formatting

### 2021-05-18 scripts/data_format.Rmd
update supp figs
clean up code

Packages
```{r}
library(tidyverse)
library(magrittr)
library(vegan)
library(patchwork)
library(ggnewscale)
library(here)
```

Data
```{r}
here()
data <- read_csv(here("data/weighted_prev_competence_111220.csv"))
names <- read_csv(here("data/species_names_ids.csv"))
```

@@

>>>>

Packages
```{r}
library(tidyverse)
library(magrittr)
library(vegan)
library(patchwork)
library(ggnewscale)
library(ape)
library(rotl)
library(here)
```

Data
```{r}
here()
data <- read_csv(here("data/weighted_prev_competence_111220.csv"))
tree <- ape::read.nexus(here("data/asup_just_tree.txt"))
names <- read_csv(here("data/species_names_ids.csv"))
```

@@

Phylogeny
```{r}
resolved <- tnrs_match_names(names$tnrs_name)
resolved$unique_name <- gsub(" ", "_",resolved$unique_name)
resolved$search_string <- paste(toupper(substr(resolved$search_string, 1, 1)), 
                                  substr(resolved$search_string,2,nchar(resolved$search_string)),sep = "")

resolved %<>% rename("species_name" = "search_string") %>% select(species_name, unique_name, ott_id)

names %<>% left_join(.,resolved)

names %<>% filter(tnrs_name!="Dryophytes avivoca") #drop species because there is no abundance data
mySpp <- c(union(names$tnrs_name,names$species_name),"Bufo terrestris") #make vector for all species names
mySpp <- gsub(" ","_",mySpp)
getRid <- setdiff(tree$tip.label,mySpp)
pruned_tree <- drop.tip(tree,getRid)
